---
title: "Lab 11 - So what if you smoke when pregnant?"
author: "Cat Seitz"
date: "03.16.23"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}

library(tidyverse) 
library(infer)
library(knitr)
library(openintro)
library(scales)
library(tidymodels)

```

```{r set-seed}

set.seed(1234)

```

```{r load-data}

data(ncbirths)

```


### Exercise 1

This data set contains 1000 observations of births in North Carolina with 13 variables, including the parents ages, the maturity of the mother (whatever that means), length of pregnancy and classification, weight of baby and classification, weight gained by mother, number of hospital visits pre-birth, baby's gender, whether the mother is white, a smoker, and is married. The ages, weeks, # of visits, and weight variables are numeric. The rest are categorical. As for outliers, it seem a little strange that a pregnant individual wouldn't gain any weight, but given that a fairly large amount of participants in this study report that, I guess it is fine. Other than that, there doesn't seem to be any crazy outliers. 

### Exercise 2

```{r filtered-df}

ncbirths_white <- ncbirths%>%
  filter(whitemom=="white")

```

```{r calc-mean-white-baby}

mean(ncbirths_white$weight)

```

The mean birth weight of our sample of Caucasian babies is 7.25, which is obviously not 7.43. 


### Exercise 3

Not sure what this is asking. But, why couldn't/wouldn't we just do a t-test here? Just to be more accurate?

```{r t-test}

t.test(ncbirths_white$weight, mu=7.43)

```


### Exercise 4




```{r boots}

boot_df<-ncbirths_white %>%
  specify(response=weight) %>%
  generate(rep=1000, type="bootstrap") %>%
  calculate(stat="mean")
```

```{r plot-boot-weight}

ggplot(data = boot_df, mapping = aes(x = stat)) +
  geom_histogram(binwidth = .01) +
  labs(title = "Bootstrap distribution of means")+
  geom_vline(xintercept = 7.145508,color = "lightblue", linewidth=2)+
  geom_vline(xintercept = 7.352768,color = "lightblue", linewidth=2)

```

```{r conf-interval-weight}

boot_df %>%
  summarize(lower = quantile(stat, 0.025),
            upper = quantile(stat, 0.975))

```


```{r add-column-shifting-means}

boot_df<- boot_df%>%
  mutate(shift=stat+.180862)

```


```{r t-test-2-columns}

t.test(boot_df$stat, boot_df$shift, paired=FALSE, var.equal=TRUE)

```

The average weight of white babies now is lower than the average weight of white babies in 1995. 

### Exercise 5 & 6

I did exercise 6 (taking out NAs) before I knew what it was. 

```{r drop-na}

ncbirths<-ncbirths %>% drop_na(habit)

```

```{r plot-smoking-mothers}

ggplot(ncbirths, aes(habit, weight, fill=habit)) +
  geom_bar(stat="summary", position="dodge") +
  xlab("Smoking Habit") + ylab("Baby Weight (lbs)") +
  scale_fill_brewer(palette="Dark2") +
  theme(legend.position="none")

```

### Exercise 7

Null hypothesis: There is no difference in babies born to smokers and nonsmokers. 

```{r new-df}

ncbirths_habit<- ncbirths %>%
  subset(select=c(weight, habit))

```

### Exercise 8 

Still don't really understand what this question is asking. 

```{r peek}

ncbirths_habitgiven<- ncbirths_habit %>%
  group_by(habit) %>%
  summarise(mean_weight = mean(weight))

```

Looks like babies born to nonsmokers are heavier than babies born to smokers. 

### Exercise 9


```{r boots}

# take 1000 bootstrap samples
habit_boot <- bootstraps(ncbirths_habit, times = 1000)

# for each sample
# fit a model and save output in model column
# tidy model output and save in coef_info column 
habit_models <- habit_boot %>%
  mutate(
    model = map(splits, ~ lm(weight ~ habit, data = .)),
    coef_info = map(model, tidy)
  )
# unnest coef_info (for intercept and slope)
habit_coefs <- habit_models %>%
  unnest(coef_info)

```

```{r calc-p}

habit_coefs %>%
  group_by(term)%>%
  summarise(mean_est=mean(estimate))

```

If a mother is a smoker, then the baby will likely weigh .31 pounds less than a baby born to a non-smoking mother. 

To calculate a p-value, we can create a data frame with our bootstrapping estimates, add a column that adds the mean to each estimate, and run a t-test to calculate if there was a difference?

```{r make-df-for-p}

habit_test <- habit_coefs%>%
  select(c(term, estimate))%>%
  filter(term == "habitsmoker") %>%
  mutate(same_est= estimate + .318)

```

```{r t-test-2-columns}

t.test(habit_test$estimate, habit_test$same_est, paired=FALSE, var.equal=TRUE)

```

Based on these results, the slope are significantly different. 

### Exercise 10

```{r confidence-interval}
# calculate 95% (default) percentile interval
int_pctl(habit_models, coef_info)

```

We are 95% confident that smokers have babies that are between 0.060-0.582 pounds lighter than non-smokers. 


### Exercise 11

Based off looking at the data, I found that older moms are ages 35+ and younger moms are less than 35 years old. 


### Exercise 12
























